A Real-Time Sonar Simulator for Automatic Target Recognition

### 2015-10-08 Simulator/article.tex
la2pdf commit - 2015:10:08	10:53:43	(Thu 8.Oct)

\begin{figure*}[t]\centering%
\subfloat[SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.]{%
\graphicsAI[drawing,width=0.5\linewidth]{gfx/data_cylinder_submerged.svg}%
\label{data_cylinder}}%
\subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
\graphicsAI[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\label{sim_cylinder}}%
\caption{A SAS image of a cylinder and a template simulation adapted to it.}
\end{figure*}

% \newcommand\cdesc[2]{{\raggedright\setlength\fboxsep{0pt}
% \fbox{\colorbox[HTML]{#1}{\vrule height8.5pt depth3.5pt width0pt\hspace{.5cm}}}\ \ #2\\}}

\newcommand\cdesc[2]{#2}

BS!!!

\begin{figure*}[t]\centering%

\subfloat[Best template out of a predefined set. Inaccurate cylinder length, alignment and immersion depth. The segmented shadow and highlight regions are misaligned.]{
\graphicsAI[drawing,width=.5\linewidth]{gfx/overlay_cylinder_submerged.svg}\label{overlay_cylinder}%
}%
\hfil%
\subfloat[Adapted template. Template simulated with adapted parameters. Good fit in both highlight and shadow segments.]{%
\graphicsAI[width=.5\linewidth]{gfx/overlay_cylinder_submerged_adaptive.svg}%
}\caption[LoF entry]{Segmented simulation image overlaid the segmented SAS image. Segmentation overlay color description:\parbox{1cm}{\small\centering 1}}%
% % \hfill
% \parbox{1cm}{\small\centering
% \newline\centering\newline %\\[.5\baselineskip]
\begin{minipage}{.35\linewidth}
% \cdesc{800000}{Template highlight and image highlight}
% \cdesc{FF1000}{Template highlight only}
% \cdesc{FFEB00}{Image highlight only}
% \cdesc{83FF7C}{Background pixels}
\end{minipage}%
% \begin{minipage}{.35\linewidth}
% \cdesc{000083}{Template shadow and image shadow}
% \cdesc{0014FF}{Template shadow only}
% \cdesc{00EFFF}{Image shadow only}
% \cdesc{00A7FF}{Template shadow and image highlight}
% \end{minipage}
% }\label{overlay_cylinder_adaptive}%
% % \vspace{\baselineskip}
\caption{Segmented simulation image overlaid the segmented SAS image.}
\end{figure*}

>>>>

\begin{figure*}[!tbp]\centering%
\subfloat[SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.]{%
\graphicsAI[drawing,width=0.5\linewidth]{gfx/data_cylinder_submerged.svg}%
\label{data_cylinder}}%
\subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
\graphicsAI[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\label{sim_cylinder}}%
\caption{A SAS image of a cylinder and a template simulation adapted to it.}
\end{figure*}

\newcommand\cdesc[2]{{\raggedright\setlength\fboxsep{0pt}
\fbox{\colorbox[HTML]{#1}{\vrule height8.5pt depth3.5pt width0pt\hspace{.5cm}}}\ \ #2\\}}

% \newcommand\cdesc[2]{#2}

\begin{figure*}[!tbp]\centering%
\subfloat[Best template out of a predefined set. Inaccurate cylinder length, alignment and immersion depth. The segmented shadow and highlight regions are misaligned.]{
\graphicsAI[drawing,width=.48\linewidth]{gfx/overlay_cylinder_submerged.svg}\label{overlay_cylinder}%
}%
\hfill%
\subfloat[Adapted template. Template simulated with adapted parameters. Good fit in both highlight and shadow segments.]{%
\graphicsAI[width=.48\linewidth]{gfx/overlay_cylinder_submerged_adaptive.svg}%
}\caption[LoF entry]{\raggedright Simulation image overlaid the segmented SAS image. Segmentation overlay color description:

\parbox{\linewidth}{\small\centering\vspace{.5\baselineskip}
% \newline\centering\newline %\\[.5\baselineskip]
\begin{minipage}{.4\linewidth}
\cdesc{800000}{Template highlight and image highlight}
\cdesc{FF1000}{Template highlight only}
\cdesc{FFEB00}{Image highlight only}
\cdesc{83FF7C}{Background pixels}
\end{minipage}%
\begin{minipage}{.4\linewidth}
\cdesc{000083}{Template shadow and image shadow}
\cdesc{0014FF}{Template shadow only}
\cdesc{00EFFF}{Image shadow only}
\cdesc{00A7FF}{Template shadow and image highlight}
\end{minipage}
}}
% }\label{overlay_cylinder_adaptive}%
% % \vspace{\baselineskip}
% \caption{Segmented simulation image overlaid the segmented SAS image.}
\end{figure*}
